Quality Definitions of Qualities

### 2021-10-09 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
added modifiability definitions

>>>>

\begin{defn}
\begin{enumerate}
	\item Ease with which a system can be changed without introducing defects.
	\item Degree to which a product or system can be effectively and efficiently modified without introducing defects or degrading existing product quality \citep{iso2017iec}.
\end{enumerate}
\end{defn}

\begin{defn}
Modifiability is about the cost of change and refers to the ease with which a software system can accommodate changes \citep{northrop2004achieving}.
\end{defn}
